Fitting Synchrotron Models to Gamma-Ray Burst Data from INTEGRAL/SPI

### 2021-12-17 src/ms.tex
H->h

% Main body with filler text
\section{Introduction}
Gamma-Ray Bursts (GRBs) are short transient bursts of gamma rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays. After the prompt emission, there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM). Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars, whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars. In both cases it is commonly agreed on, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions. But it is still highly debated what the exact emission mechanism of the Gamma-Rays is. \citep{gamma-ray-burst, gw}

@@

Generally PySPI can improve the scientific output from SPI for GRBs significantly. Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
\begin{appendix}
  \section{Model Checking Plots}
  \label{appendix1}
  In this section we show a selection of the PPC- and QQ-plots for the simultaneous synchrotron fit to the SPI and GBM data for GRB120711A.
  \begin{figure}[h]
    \begin{centering}
      \includegraphics[width=0.45\linewidth]{figures/n0_ppc.pdf}
      \includegraphics[width=0.45\linewidth]{figures/n0_qq.pdf}
      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.}
      \label{fig:n0_model_check}
    \end{centering}
  \end{figure}
  \begin{figure}[h]
    \begin{centering}
      \includegraphics[width=0.45\linewidth]{figures/b0_ppc.pdf}
      \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.}
      \label{fig:b0_model_check}
    \end{centering}
  \end{figure}
  \begin{figure}[h]
    \begin{centering}
      \includegraphics[width=0.45\linewidth]{figures/low_13_ppc.pdf}
      \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
      \label{fig:low_13_model_check}
    \end{centering}
  \end{figure}
  \begin{figure}[h]
    \begin{centering}
      \includegraphics[width=0.45\linewidth]{figures/psd_13_ppc.pdf}
      \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
      \label{fig:psd_13_model_check}
    \end{centering}
  \end{figure}
\end{appendix}

\bibliographystyle{aasjournal}
\bibliography{biblio}

>>>>

% Main body with filler text
\section{Introduction}

Gamma-Ray Bursts (GRBs) are short transient bursts of gamma rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays. After the prompt emission, there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM). Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars, whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars. In both cases it is commonly agreed on, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions. But it is still highly debated what the exact emission mechanism of the Gamma-Rays is. \citep{gamma-ray-burst, gw}

@@

Generally PySPI can improve the scientific output from SPI for GRBs significantly. Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.

\begin{appendix}
  \section{Model Checking Plots}
  \label{appendix1}
  In this section we show a selection of the PPC- and QQ-plots for the simultaneous synchrotron fit to the SPI and GBM data for GRB120711A.
  \begin{figure}[h]
    \begin{centering}
      \includegraphics[width=0.45\linewidth]{figures/n0_ppc.pdf}
      \includegraphics[width=0.45\linewidth]{figures/n0_qq.pdf}
      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.}
      \label{fig:n0_model_check}
    \end{centering}
  \end{figure}
  \begin{figure}[h]
    \begin{centering}
      \includegraphics[width=0.45\linewidth]{figures/b0_ppc.pdf}
      \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.}
      \label{fig:b0_model_check}
    \end{centering}
  \end{figure}
  \begin{figure}[h]
    \begin{centering}
      \includegraphics[width=0.45\linewidth]{figures/low_13_ppc.pdf}
      \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
      \label{fig:low_13_model_check}
    \end{centering}
  \end{figure}
  \begin{figure}[h]
    \begin{centering}
      \includegraphics[width=0.45\linewidth]{figures/psd_13_ppc.pdf}
      \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
      \label{fig:psd_13_model_check}
    \end{centering}
  \end{figure}
\end{appendix}

\bibliographystyle{aa}
\bibliography{biblio}
